Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-25 ms.tex
pca eigenvector plots for individual amplifiers

\subsubsection{Smoothed Kernel Subtraction}

@@

\subsubsection{PCA Correction}
Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
Here, we assume that each column is a random variable that is correlated with the rest of the columns.
Each row represents a different noise iteration.
We first mask all bad pixels by setting all pixels with $| f | > 200$ DN.
The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
These first 10 principal components explain 10\% of the total variance in each group up the ramp.

@@

@@

If we treat each amplifier separately, the PCA model is more effective in reducing 1/f noise.
We begin by keeping 5 principal components within each amplifier and subtracting these from each amplifier separately.
The resulting standard deviation of the time series is 2900 to 3870 DN.

>>>>

\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}

@@

\subsubsection{PCA Correction}
Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
Here, we assume that each column is a random variable that is correlated with the rest of the columns.
Each row represents a different noise iteration.
We first mask all bad pixels by setting all pixels with $| f | > 200$ DN.
The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
These first 10 principal components explain 10\% of the total variance in each group up the ramp.
The principal components from one group to another are very similar.
\textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54.pdf}
\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55.pdf}
\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
Again, the eigenvectors are very similar other than vertical flips.
}\label{fig:pcaEigenvectors}
\end{figure*}

@@

If we treat each amplifier separately, the PCA model is more effective in reducing 1/f noise.
We begin by keeping 5 principal components within each amplifier and subtracting these from each amplifier separately.
The resulting standard deviation of the time series is 2900 to 3870 DN.
This is improvement is beyond what is possible on a real source because the principal components include pixels over the source aperture.
To simulate a real photometry scenario, it is necessary to interpolate over the source aperture points as done in Section \ref{sec:smoothKernelSub} for the smoothing kernel.
